Molecular dynamics simulation of synchronization in driven particles

### 2021-02-03 manuscript/manuscript_ajp_2020.tex
added comment to Brownian motion

  \begin{center}
    \begin{figure}[h!]
      \centering
      \includegraphics[width=\columnwidth]{{brownian_particle_dt0.1}.pdf}
      \caption{
        Motion of a particle undergoing Brownian motion
        on a washboard potential
        energy landscape.
        (a) $T/A_p = 4.0$ no hopping occurs.
        (b) $T/A_p = 5.0$ a single hop occurs at $t = 130000$
        (c) $T/A_p = 6.0$ many hops occur.
        Note the scale of the $y-$axis differs in each panel.
      }
      \label{fig:brownian}
    \end{figure}
  \end{center}
  In Fig.~\ref{fig:brownian}
  we show the position versus time of a particle
  confined to a sinusoidal landscape
  undergoing Brownian motion.
  We increase the temperature relative
  to the amplitude of the landscape
  troughs until the particle enters a hopping regime.
  In  Fig.~\ref{fig:brownian}(a)
  $T/A_p = 4.0$ and the particle executes a 
  random walk centered at the potential minima $y/\lambda = 10$.
  We ran many simulations and never observed a hop to another minima.
  In  Fig.~\ref{fig:brownian}(b)
  $T/A_p = 5.0$ where hops between
  potential minima are possible but not probable,
  a single hop occurs from
  $y/\lambda = 10$ to $y/\lambda = 11$ at
  $t \sim 13000 \tau$.
  In other simulations with identical parameters,
  we sometimes observed no hops or two hops between minima,
  as expected with random fluctuating systems.
  In  Fig.~\ref{fig:brownian}(c)
  $T/A_p = 6.0$ 
  we observe approximately 15 hops,
  indicating the random thermalized kicks are
  sufficiently large to make the particle perform
  a random walk of hops a top the substrate
  in addition to the small scale random walk executed
  by all particles in this section.

@@

  In Fig.~\ref{fig:hops_back}
  we show the results for increasing $F^{ac}$
  of the system for our original parameters.
  Here $n_b$ increases from $n_b = 0$ in (a) to

>>>>

  \begin{center}
    \begin{figure}[h!]
      \centering
      \includegraphics[width=\columnwidth]{{brownian_particle_dt0.1}.pdf}
      \caption{
        Motion of a particle undergoing Brownian motion
        on a washboard potential
        energy landscape.
        (a) $T/A_p = 4.0$ no hopping occurs.
        (b) $T/A_p = 5.0$ a single hop occurs at $t = 130000$
        (c) $T/A_p = 6.0$ many hops occur.
        Note the scale of the $y-$axis differs in each panel
        and the time scale on the $x-$axis is
        much greater than the period in Fig.~\ref{fig:1}.
      }
      \label{fig:brownian}
    \end{figure}
  \end{center}
  In Fig.~\ref{fig:brownian}
  we show the position versus time of a particle
  confined to a sinusoidal landscape
  undergoing Brownian motion.
  We increase the temperature relative
  to the amplitude of the landscape
  troughs until the particle enters a hopping regime.
  In  Fig.~\ref{fig:brownian}(a)
  $T/A_p = 4.0$ and the particle executes a 
  random walk centered at the potential minima $y/\lambda = 10$.
  We ran many simulations and never observed a hop to another minima.
  In  Fig.~\ref{fig:brownian}(b)
  $T/A_p = 5.0$ where hops between
  potential minima are possible but not probable,
  a single hop occurs from
  $y/\lambda = 10$ to $y/\lambda = 11$ at
  $t \sim 13000 \tau$.
  In other simulations with identical parameters,
  we sometimes observed no hops or two hops between minima,
  as expected with random fluctuating systems.
  In  Fig.~\ref{fig:brownian}(c)
  $T/A_p = 6.0$ 
  we observe approximately 15 hops,
  indicating the random thermalized kicks are
  sufficiently large to make the particle perform
  a random walk of hops a top the substrate
  in addition to the small scale random walk executed
  by all particles in this section.
  At these temperatures the rate
  of hopping is much less than the
  frequency of the applied drive and synchronized motion,
  so the effects of temperature are may ignored
  in these simulations.

@@

  In Fig.~\ref{fig:hops_back}
  we show the results for increasing $F^{ac}$
  of the system for our original parameters.
  Here $n_b$ increases from $n_b = 0$ in (a) to
  $n_b = 2$ in (b) to $n_b = 4$ in (c).
